\documentclass[11pt,a4paper,openany,twoside,english,titlepage=true]{scrbook}
%\enabledeprecatedfontcommands
\input{Tex/pakete}
%\input{Tex/literatur}
%\input{Tex/glossar}
%\input{Tex/gestaltung}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RE,LO]{\thepage}
\fancyhead[LE]{\textsl{\rightmark}}
\fancyhead[RO]{\textsl{\leftmark}}
\renewcommand{\headrulewidth}{1pt}
\fancyfoot{}
% use "pagestyle" also on chapter starting pages
\renewcommand{\chapterpagestyle}{fancy}
\usepackage[Sonny]{fncychap}
\RedeclareSectionCommand[beforeskip=0pt,
afterskip=2cm]{chapter}

\newcounter{Seitenzahl}%Nummerierung: Roman (bis einschl. Verzeichnisse), Arabic (Haptteil+Appendix), Roman (Literaturverzeichnis)

%-----------------eigene Befehle------------------------
\newcommand{\abstrakt}[1]{\chapter*{#1}\addcontentsline{toc}{chapter}{#1}}

%-----------------überschriebene Befehle----------------


%--------------Titelpage (see titelseity.sty)-----------
\project{PhD-Thesis}
\author{Jason W. Sidabras}
\title{Improving Electron Paramagnetic Resonance Performance by Time-Varying Magnetic Field Manipulation.}
\supervisor{Prof. Dieter Suy ter: TU Dortmund\\ Prof. Wolfgang Lubitz: MPI-CEC}

%-----------------begin document------------------------
\CitationPrefix{\thechapter.}



\begin{document}
\raggedbottom
\pagenumbering{Roman}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%							Titelseite
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%							Abstract (and other pre-TOC-stuff)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Kapitel/Abstract_EN.tex}
\input{Kapitel/Abstract_DE.tex}
\input{Kapitel/Danksagung.tex}

\newpage
\chapter*{List of Publications}

\textbf{Scientific Publications in this work: }
\begin{enumerate}
\itemsep0em
    \item \textbf{\underline{J.~W.~Sidabras}}, T.~Sarna, R.~R.~Mett, J.~S.~Hyde, {\em Uniform field loop-gap
  resonator and rectangular {TE}$_{\text{{U}02}}$ for aqueous sample {EPR} at 94~{GHz}}, J. Magn. Reson. 282 (2017) 129--135.
    \item \textbf{\underline{J.~W.~Sidabras}}, E.~J.~Reijerse, W.~Lubitz, {\em Uniform field re-entrant cylindrical
  {TE}$_{\text{01{U}}}$ cavity for pulse electron paramagnetic resonance spectroscopy at {Q}-band}, Appl. Magn. Reson. 48~(11) (2017) 1301--1314.
    \item J.~S.~Hyde, \textbf{\underline{J.~W. Sidabras}}, R.~R. Mett, {\em Uniform field resonators for {EPR}
  spectroscopy: A review}, Cell Biochem. Biophys. 76~(1-2) (2018) 1--12.
    \item \textbf{\underline{J.~W.~Sidabras}}, J.~Duan, M.~Winkler, T.~Happe, R.~Hussein, A.~Zouni, D.~Suter,
  A.~Schnegg, W.~Lubitz, E.~J.~Reijerse, {\em Improving Electron Paramagnetic Resonance Sensitivity for nano-Liter Volume Single-Crystals Using a Self-Resonant micro-Helix}., Sci. Adv., {\em Accepted}.
    \item \textbf{\underline{J.~W.~Sidabras}}, J.~Nehrkorn, R.~Narkowicz, K.~Holldack, D.~Suter,
  A.~Schnegg, {\em Weak Coupling of Meta-Materials with Ensemble of Electron Spins: Surface EPR Signal Enhancement in the THz Bandgap}., {\em in preparation}.
\end{enumerate}

\chapter*{List of Presentations}
\begin{enumerate}
\itemsep0em 
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, W.~Lubitz (2016). {\em Resonator Development for Studying Protein Single Crystals of Limited Dimensions}. Xth International Workshop on EPR (ESR) in Biology and Medicine, Krakow, Poland (Invited Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, W.~Lubitz (2016). {\em Micro-Resonators for Electron Paramagnetic Resonance Spectroscopy of Size Limited Samples at 9.5 GHz}. German Chemical Society (GDCh), Magnetic Resonance Section (FGMR) 38th Annual Discussion Meeting, Düsseldorf, DE  (Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, W.~Lubitz (2017). {\em Multi-Frequency Resonator Development for Studying Volume-Limited Metallo-Proteins}. 2nd Adriatic Symposium on Byophysical Approaches in Biomedical Studies, Split, Croatia (Invited Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, A.~Savitsky, W.~Lubitz (2017). {\em Resonator Development for Studying Protein Single Crystals of Limited Dimensions at X-band}. 20th ISMAR and Rocky Mountain Conference on EPR, Quebec City, Quebec, Canada (Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, W.~Lubitz (2017). {\em Multi-Frequency Resonator Development}. International Conference on Electron Paramagnetic Resonance Spectroscopy and Imaging of Biological Systems EPR 2017, Morgantown, WV (Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, A.~Savitsky, W.~Lubitz (2017). {\em Planar Micro-Resonators and Micro-Helix Geometries for Studying Protein Single Crystals with X-band EPR}. 50th International International Meeting of the ESR Spectroscopy Group of the Royal Society of Chemistry, Oxford, UK (Talk)
    \item J.~W.~Sidabras, E.~J.~Reijerse, W.~Lubitz (2018). {\em Uniform Field Resonators for Correlation Spectroscopy Methods at Q-Band}. 51st Annual International Meeting ESR Spectroscopy Group of the Royal Society of Chemistry, London, UK (Talk)
    \item J.~W.~Sidabras (2019). {\em Beyond structure: Investigating paramagnetic states in protein crystals of nano-liter volumes at X band}. XIth International Workshop on EPR (ESR) in Biology and Medicine, Krakow, Poland (Invited Talk)
\end{enumerate}

\chapter*{List of Poster Presentations}
\begin{enumerate}
\itemsep0em 
    \item J.~W.~Sidabras, E.~J.~Reijerse, C.~Sommer, J.~Duan, M.~Winkler, T.~Happe, D.~Suter, W.~Lubitz (2019) {\em Technical Advances in Order to Study nano-Liter Volume [FeFe]-Hydrogenase Single Crystals using Electron Paramagnetic Resonance}, 12th International Hydrogenase Conference, Lisbon, Portugal (Poster)
    \item J.~W.~Sidabras, E.~J.~Reijerse, J.~Duan, M.~Winkler, T.~Happe, A.~Schnegg, D.~Suter, W.~Lubitz (2019) {\em A Self-Resonant Micro-Helix for Studying nano-Liter Volume [FeFe]-Hydrogenase Single-Crystals using CW and Pulse EPR Techniques}, EUROMAR 2019, ISMAR 2019, and the 41st GDCh FGMR Joint Conference, Berlin, Germany (Poster)
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%						Verzeichnisse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addcontentsline{toc}{chapter}{Table of Contents}
\makeatletter
\renewcommand{\@pnumwidth}{1.75em} 
\renewcommand{\@tocrmarg}{2em}
\makeatother
\tableofcontents\newpage

\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures\newpage

\addcontentsline{toc}{chapter}{List of Tables}
\listoftables\newpage

\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%							Hauptteil
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cleardoublepage
\setcounter{Seitenzahl}{\value{page}}
\setcounter{page}{0}
\pagenumbering{arabic}
\mainmatter


\include{Kapitel/Ch1-Einleitung}
\include{Kapitel/Ch2-TheoryExperimental}
\include{Kapitel/Ch3-UniformField}
\include{Kapitel/Ch4-THzSRR}
\include{Kapitel/Ch5-MicroHelix}
\include{Kapitel/Ch6-FeFeHydrogenase}
\include{Kapitel/Ch7-ConclusionsOutlook}
\begin{appendices}
\include{Kapitel/Appendix1-FEM}
\include{Kapitel/Appendix2-MathamaticaCode}
\include{Kapitel/Appendix3-MatLabCode}
\include{Kapitel/Appendix4-ESEEM}
\end{appendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%						Literaturverzeichnis
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\backmatter
\pagenumbering{Roman}
%\setcounter{page}{\theSeitenzahl}
%\addcontentsline{toc}{chapter}{\bibname}%je nach Klasse evtl. 'section' durch 'chapter' ersetzten
%\sloppy
%\printbibliography


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%							Anhang
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{appendices}
%	\include{Kapitel/Anhang}
%	\include{Kapitel/Anhang2}
%\end{appendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%							Glossary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\printglossary[style=index]
%\printglossary[type=\acronymtype,style=index]
%\printglossary[type=symbols,style=index]
%\printindex
	
\end{document}