\chapter[\textit{Curriculum Vitae}.]{\textit{Curriculum Vitae}}
\vspace{-4em}
\noindent {\Huge Jason W. Sidabras} 
\vspace{1em}

\begin{tabular}{ll}
DOB:        &   10 November, 1981 \\
Websites:   &   https://jasonsidabras.com \\
            &   https://act-epr.org \\
Email:      &   jason.sidabras@cec.mpg.de \\
            &   jason.sidabras@gmail.com
\end{tabular}

\subsection*{Research}
\vspace{-0.5em}
\textbf{Max Planck for Chemical Energy Conversion}\\
\textit{EU Researcher}
\small{March 2016 – Present | Biophysical Chemistry | M{\"u}lheim a.d. Ruhr, DE \\
Supervisor: Prof. Wolfgang Lubitz \\
Summary: 2 Papers, 8 Talks, 3 Abstracts}
\vspace{-0.5em}
\begin{itemize}
\setlength\itemsep{-0.5em}
    \item Awarded the Horizon 2020 Marie Sk\l{}odowska-Curie Actions Fellowship
    \item Develop resonators for micro-crystals to study [FeFe]-Hydrogenase
    \item Developing novel resonators from 10~GHz to 244~GHz
\end{itemize}

\noindent\textbf{Medical College of Wisconsin}\\
\textit{Research Engineer III}
\small{June 2003 – February 2016 | Dept. of Biophysics | Milwaukee, WI, USA \\
Supervisor: Prof. James S. Hyde \\
Summary: 31 Papers, 1 Book Chapter, 3 Patents, 7 Talks, and 35 Abstracts}
\vspace{-0.5em}
\begin{itemize}
\setlength\itemsep{-0.5em}
    \item Uniform 100~kHz field modulation for cylindrical TE$_{011}$ cavities
    \item Dual loop-gap resonator for pulse experiments at 94 GHz
    \item Optimized PTFE extrusions, taking advantage of the properties of having the sample placed in a perpendicular orientation to the electric field, resulting in EPR signal improvements
    \item EPR and MRI resonator development (250 MHz–260 GHz)
\end{itemize}

\subsection*{Education} 
\vspace{-0.5em}
\noindent\textbf{Technical University Dortmund} \\
\textit{Physics} 2016-2019 | Dortmund, DE \\
Supervisor: Prof. Dieter Suter 
\newline

\noindent\textbf{Medical College of Wisconsin} \\
\textit{BioPhysics} 2015-2016 | Milwaukee, WI | Cum. GPA: 3.56 \\
Supervisor: Prof. James S. Hyde
\vspace{-0.5em}
\begin{itemize}
\setlength\itemsep{-0.5em}
    \item Formal course in Magnetic Resonance in context with new developments of spin-labeling
    \item Formal course in biophysical principles of cellular functions 
\end{itemize}

\noindent\textbf{Marquette University} \\
\textit{M.S. in Electrical Engineering} 2004-2010 | Milwaukee, WI | Cum. GPA: 3.31 \\
Supervisor: Profs. James E. Richie \& James S. Hyde
Thesis: Modelling Electron Paramagnetic Resonance Field-Modulation Slots using Dyadic Green Functions of Evanescent Fields in Rectangular and Cylindrical Waveguides
\vspace{-0.5em}
\begin{itemize}
\setlength\itemsep{-0.5em}
    \item Studied fundamentals of numerical methods
    \item Further refined analytical skills in electromagnetic theory 
\end{itemize}

\noindent\textbf{Milwaukee School of Engineering}\\
\textit{B.S. in Electrical Engineering Technology}
1999-2003 | Milwaukee, WI
\vspace{-0.5em}
\begin{itemize}
\setlength\itemsep{-0.5em}
    \item Studied fundamentals of electrical engineering principles: focused on electromagnetics
\end{itemize}

\subsection*{Awards} 
\vspace{-0.5em}
\begin{tabular}{cl}
2017-2019 & Horizon 2020 Marie Sk\l{}odowska-Curie Actions Fellowship\\
2017 	& 21st annual JEOL Student Lecture Competition Winner\\
2017 	& EPR2017 Young Investigator Award of Excellence Prize\\
\end{tabular}

\subsection*{Societies} 
\vspace{-0.5em}
\begin{tabular}{rll}
2009 	& U.S. National    & Sigma Xi: Scientific research\\
2012   & International   & International EPR (ESR) Society\\
2015   &  International  & Advancing Science, Serving Society (AAAS)\\
\end{tabular}

\subsection*{Patents} 
\vspace{-0.5em}
\begin{tabular}{rll}
2006   & U.S. \#7,088,101   & \begin{tabular}{l}
Aqueous sample holder for electron paramagnetic \\
resonance and magnetic resonance spectroscopy.
\end{tabular}\\
2014 	& U.S. \#8,674,694    & \begin{tabular}{l}
Coil System and Method for Post-Exposure Dosimetry \\
 Using Electron Paramagnetic Resonance Spectroscopy.
\end{tabular}\\
2017 	& PCT.US2017-052045    & \begin{tabular}{l}
Strongly coupled fourth-order resonance coil systems \\
for enhanced signal detection 
\end{tabular}
\end{tabular}


\subsection*{List of Publications}
\begin{enumerate}
\itemsep0em 
    \item \underline{Sidabras, J. W.}, Duan, J., Winkler, M., Happe, T., Hussein, R., Zouni, A., Suter, D., Schnegg, A., Lubitz, W. and Reijerse, E. J. \textit{Extending electron paramagnetic resonance to nanoliter volume protein single crystals using a self-resonant microhelix.,} Sci. Adv. (5), 2019, pp. eaay1394.
    \item Hyde, J. S., \underline{Sidabras, J. W.} and Mett, R. R. \textit{Uniform Field Resonators for EPR Spectroscopy: A Review.,} Cell Biochem. Biophys. (77), 2019, pp. 3--14.
    \item Mett, R. R., \underline{Sidabras, J. W.}, Anderson, J. R., Klug, C. S. and Hyde, J. S. \textit{Rutile dielectric loop-gap resonator for X-band EPR spectroscopy of small aqueous samples.,} J. Magn. Reson. (307), 2019, pp. 106585.
    \item Zadlo, A., Szewczyk, G., Sarna, M., Camenisch, T. G., \underline{Sidabras, J. W.}, Ito, S., Wakamatsu, K., Sagan, F., Mitoraj, M. and Sarna, T. \textit{Photobleaching of pheo\-/melanin increases its phototoxic potential: Physicochemical studies of synthetic pheomelanin subjected to aerobic photolysis.,} Pigment Cell Melanoma Res. (32), 2019, pp. 359--372.
    \item Swarts, S. G., \underline{Sidabras, J. W.}, Grinberg, O., Tipikin, D. S., Kmiec, M., Petryakov, S. V., Schreiber, W., Wood, V. A., Williams, B. B., Flood, A. B. and Swartz, H. M. \textit{Developments in Biodosimetry Methods for Triage With a Focus on X-band Electron Paramagnetic Resonance In Vivo Fingernail Dosimetry.,} Health Phys. (115), 2018, pp. 140--150.
    \item \underline{Sidabras, J. W.}, Mett, R. R. and Hyde, J. S. \textit{Extruded dielectric sample tubes of complex cross section for EPR signal enhancement of aqueous samples.,} J. Magn. Reson. (277), 2017, pp. 45--51.
    \item \underline{Sidabras, J. W.}, Reijerse, E. J. and Lubitz, W. \textit{Uniform Field Re-entrant Cylindrical TE$_{01U}$ Cavity for Pulse Electron Paramagnetic Resonance Spectroscopy at Q-band.,} Appl. Magn. Reson. (48), 2017, pp. 1301--1314.
    \item \underline{Sidabras, J. W.}, Richie, J. E. and Hyde, J. S. \textit{Axially uniform magnetic field-modulation excitation for electron paramagnetic resonance in rectangular and cylindrical cavities by slot cutting.,} J. Magn. Reson (274), 2017, pp. 115--124.
    \item \underline{Sidabras, J. W.}, Sarna, T., Mett, R. R. and Hyde, J. S. \textit{Uniform field loop-gap resonator and rectangular TE$_{U02}$ for aqueous sample EPR at 94GHz.,} J. Magn. Reson (282), 2017, pp. 129--135.
    \item Strangeway, R. A., Hyde, J. S., Camenisch, T. G., \underline{Sidabras, J. W.}, Mett, R. R., Anderson, J. R., Ratke, J. J. and Subczynski, W. K. \textit{Broadband W-band Rapid Frequency Sweep Considerations for Fourier Transform EPR.,} Cell Biochem. Biophys. (75), 2017, pp. 259--273.
    \item Grinberg, O., \underline{Sidabras, J. W.}, Tipikin, D. S., Krymov, V., Mariani, M., Feldman, M. M., Kmiec, M. M., Petryakov, S. V., Brugger, S., Carr, B., Schreiber, W., Swarts, S. G. and Swartz, H. M. \textit{Dielectric-Backed Aperture Resonators for X-Band in vivo EPR Nail Dosimetry.,} Radiat. Prot. Dosim. (172), 2016, pp. 121--126.
    \item Mett, R. R., \underline{Sidabras, J. W.} and Hyde, J. S. \textit{MRI surface-coil pair with strong inductive coupling.,} Rev. Sci. Instrum. (87), 2016, pp. 124704.
    \item Mett, R. R., \underline{Sidabras, J. W.} and Hyde, J. S. \textit{Meta-metallic coils and resonators: Methods for high Q-value resonant geometries.,} Rev. Sci. Instrum. (87), 2016, pp. 084703.
    \item \underline{Sidabras, J. W.}, Strangeway, R. A., Mett, R. R., Anderson, J. R., Mainali, L. and Hyde, J. S. \textit{Hyperbolic-cosine waveguide tapers and oversize rectangular waveguide for reduced broadband insertion loss in W-band electron paramagnetic resonance spectroscopy. II. Broadband characterization.,} Rev. Sci. Instrum. (87), 2016, pp. 034704.
    \item Tipikin, D. S., Swarts, S. G., \underline{Sidabras, J. W.}, Trompier, F. and Swartz, H. M. \textit{Possible nature of the radiation-induced signal in nails: High-field EPR, confirming chemical synthesis, and quantum chemical calculations.,} Radiat. Prot. Dosim. (172), 2016, pp. 112--120.
    \item Li, R., Liu, X., \underline{Sidabras, J. W.}, Paulson, E. S., Jesmanowicz, A., Nencka, A. S., Hudetz, A. G. and Hyde, J. S. \textit{Restoring susceptibility induced MRI signal loss in rat brain at 9.4 T: A step towards whole brain functional connectivity imaging.,} PLoS One (10), 2015, pp. e0119450.
    \item He, X., Swarts, S. G., Demidenko, E., Flood, A. B., Grinberg, O., Gui, J., Mariani, M., Marsh, S. D., Ruuge, A. E., \underline{Sidabras, J. W.}, Tipikin, D., Wilcox, D. E. and Swartz, H. M. \textit{Development and validation of an ex vivo electron paramagnetic resonance fingernail biodosimetric method.,} Radiat. Prot. Dosim. (159), 2014, pp. 172--181.
    \item Mainali, L., \underline{Sidabras, J. W.}, Camenisch, T. G., Ratke, J. J., Raguz, M., Hyde, J. S. and Subczynski, W. K. \textit{Spin-label W-band EPR with seven-loop-six-gap resonator: Application to lens membranes derived from eyes of a single donor.,} Appl. Magn. Reson. (45), 2014, pp. 1343--1358.
    \item \underline{Sidabras, J. W.}, Varanasi, S. K., Mett, R. R., Swarts, S. G., Swartz, H. M. and Hyde, J. S. \textit{A microwave resonator for limiting depth sensitivity for electron paramagnetic resonance spectroscopy of surfaces.,} Rev. Sci. Instrum. (85), 2014, pp. 104707.
    \item Hyde, J. S., Bennett, B., Kittell, A. W., Kowalski, J. M. and \underline{Sidabras, J. W.} \textit{Moving difference (MDIFF) non-adiabatic rapid sweep (NARS) EPR of copper(II).,} J. Magn. Reson (236), 2013, pp. 15--25.
    \item Swartz, H. M., Flood, A. B., Williams, B. B., Dong, R., Swarts, S. G., He, X., Grinberg, O., Sidabras, J., Demidenko, E., Gui, J., Gladstone, D. J., Jarvis, L. A., Kmiec, M. M., Kobayashi, K., Lesniewski, P. N., Marsh, S. D. P., Matthews, T. P., Nicolalde, R. J., Pennington, P. M., Raynolds, T., Salikhov, I., Wilcox, D. E. and Zaki, B. I. \textit{Electron paramagnetic resonance dosimetry for a large-scale radiation incident.,} Health Phys. (103), 2012, pp. 255--267.
    \item He, X., Gui, J., Matthews, T. P., Williams, B. B., Swarts, S. G., Grinberg, O., Sidabras, J., Wilcox, D. E. and Swartz, H. M. \textit{Advances towards using finger/toenail dosimetry to triage a large population after potential exposure to ionizing radiation.,} Radiat. Meas. (46), 2011, pp. 882--887.
    \item Kittell, A. W., Camenisch, T. G., Ratke, J. J., \underline{Sidabras, J. W.} and Hyde, J. S. \textit{Detection of undistorted continuous wave (CW) electron paramagnetic resonance (EPR) spectra with non-adiabatic rapid sweep (NARS) of the magnetic field.,} J. Magn. Reson (211), 2011, pp. 228--233.
    \item Mett, R. R., \underline{Sidabras, J. W.}, Anderson, J. R. and Hyde, J. S. \textit{Hyperbolic-cosine waveguide tapers and oversize rectangular waveguide for reduced broadband insertion loss in W-band electron paramagnetic resonance spectroscopy.,} Rev. Sci. Instrum. (82), 2011, pp. 074704.
    \item Pollock, J., Williams, B. B., \underline{Sidabras, J. W.}, Grinberg, O., Salikhov, I., Lesniewski, P., Kmiec, M. and Swartz, H. M. \textit{Surface loop resonator design for in vivo EPR tooth dosimetry using finite element analysis.,} Health Phys. (98), 2010, pp. 339--344.
    \item Hyde, J. S., Bennett, B., Walter, E. D., Millhauser, G. L., \underline{Sidabras, J. W.} and Antholine, W. E. \textit{EPR of Cu2+ prion protein constructs at 2 GHz using the g(perpendicular) region to characterize nitrogen ligation.,} Biophys. J. (96), 2009, pp. 3354--3362.
    \item Mett, R. R., \underline{Sidabras, J. W.} and Hyde, J. S. \textit{Coupling of Waveguide and Resonator by Inductive and Capacitive Irises for EPR Spectroscopy.,} Appl. Magn. Reson. (35), 2009, pp. 285--318.
    \item Froncisz, W., Camenisch, T. G., Ratke, J. J., Anderson, J. R., Subczynski, W. K., Strangeway, R. A., \underline{Sidabras, J. W.} and Hyde, J. S. \textit{Saturation recovery EPR and ELDOR at W-band for spin labels.,} J. Magn. Reson (193), 2008, pp. 297--304.
    \item Mett, R. R., \underline{Sidabras, J. W.}, Golovina, I. S. and Hyde, J. S. \textit{Dielectric microwave resonators in TE(011) cavities for electron paramagnetic resonance spectroscopy.,} Rev. Sci. Instrum. (79), 2008, pp. 094702.
    \item Hyde, J. S., Froncisz, W., \underline{Sidabras, J. W.}, Camenisch, T. G., Anderson, J. R. and Strangeway, R. A. \textit{Microwave frequency modulation in CW EPR at W-band using a loop-gap resonator.,} J. Magn. Reson (185), 2007, pp. 259--263.
    \item \underline{Sidabras, J. W.}, Mett, R. R., Froncisz, W., Camenisch, T. G., Anderson, J. R. and Hyde, J. S. \textit{Multipurpose EPR loop-gap resonator and cylindrical TE$_{011}$ cavity for aqueous samples at 94 GHz.,} Rev. Sci. Instrum. (78), 2007, pp. 034701.
    \item \underline{Sidabras, J. W.}, Mett, R. R. and Hyde, J. S. \textit{Aqueous flat-cells perpendicular to the electric field for use in electron paramagnetic resonance spectroscopy, II: design.,} J. Magn. Reson (172), 2005, pp. 333--341.
    \item Mett, R. R., \underline{Sidabras, J. W.} and Hyde, J. S. \textit{Radio frequency skin depth concepts in magnetic resonance,} Curr. Top. Biophys (28:2), 2004, pp. 117--122.
\end{enumerate}



\subsection*{Book Chapter}
\begin{enumerate}
\itemsep0em 
    \item Hyde, J. S. \underline{Sidabras, J. W.}, Mett, R. R., \textit{Multifrequency electron paramagnetic resonance: theory and applications}, edited by S. K. Misra (John Wiley \& Sons, 2011), Chap.~5.2: Resonators for Multifrequency EPR of Spin Labels.
\end{enumerate}

\subsection*{List of Recent Presentations}
Full list of abstracts can be found at \textit{http://jasonsidabras.com.} Internal talks at MPI-CEC, TUD, or MCW are not listed.
\begin{enumerate}
\itemsep0em 
    \item J.~W.~Sidabras (2019). {\em Beyond structure: Investigating paramagnetic states in protein crystals of nano-liter volumes at X band}. XIth International Workshop on EPR (ESR) in Biology and Medicine, Krakow, Poland (Invited Talk)
    \item J.~W.~Sidabras, E.~J.~Reijerse, W.~Lubitz (2018). {\em Uniform Field Resonators for Correlation Spectroscopy Methods at Q-Band}. 51st Annual International Meeting ESR Spectroscopy Group of the Royal Society of Chemistry, London, UK (Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, A.~Savitsky, W.~Lubitz (2017). {\em Planar Micro-Resonators and Micro-Helix Geometries for Studying Protein Single Crystals with X-band EPR}. 50th International International Meeting of the ESR Spectroscopy Group of the Royal Society of Chemistry, Oxford, UK (Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, W.~Lubitz (2017). {\em Multi-Frequency Resonator Development}. International Conference on Electron Paramagnetic Resonance Spectroscopy and Imaging of Biological Systems EPR 2017, Morgantown, WV (Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, A.~Savitsky, W.~Lubitz (2017). {\em Resonator Development for Studying Protein Single Crystals of Limited Dimensions at X-band}. 20th ISMAR and Rocky Mountain Conference on EPR, Quebec City, Quebec, Canada (Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, W.~Lubitz (2017). {\em Multi-Frequency Resonator Development for Studying Volume-Limited Metallo-Proteins}. 2nd Adriatic Symposium on Byophysical Approaches in Biomedical Studies, Split, Croatia (Invited Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, W.~Lubitz (2016). {\em Micro-Resonators for Electron Paramagnetic Resonance Spectroscopy of Size Limited Samples at 9.5 GHz}. German Chemical Society (GDCh), Magnetic Resonance Section (FGMR) 38th Annual Discussion Meeting, Düsseldorf, DE  (Talk)
    \item J.~W.~Sidabras, D.~Suter, E.~J.~Reijerse, W.~Lubitz (2016). {\em Resonator Development for Studying Protein Single Crystals of Limited Dimensions}. Xth International Workshop on EPR (ESR) in Biology and Medicine, Krakow, Poland (Invited Talk)
\end{enumerate}

\subsection*{List of Recent Poster Presentations}
Full list of abstracts can be found at \textit{http://jasonsidabras.com.} Internal posters at MPI-CEC or MCW are not listed.
\begin{enumerate}
\itemsep0em 
    \item \underline{J.~W.~Sidabras}, E.~J.~Reijerse, C.~Sommer, J.~Duan, M.~Winkler, T.~Happe, D.~Suter, W.~Lubitz (2019) {\em Technical Advances in Order to Study nano-Liter Volume [FeFe]\-/Hydrogenase Single Crystals using Electron Paramagnetic Resonance}, 12th International Hydrogenase Conference, Lisbon, Portugal (Poster)
    \item \underline{J.~W.~Sidabras}, E.~J.~Reijerse, J.~Duan, M.~Winkler, T.~Happe, A.~Schnegg, D.~Suter, W.~Lubitz (2019) {\em A Self-Resonant Micro-Helix for Studying nano-Liter Volume [FeFe]\-/Hydrogenase Single-Crystals using CW and Pulse EPR Techniques}, EUROMAR 2019, ISMAR 2019, and the 41st GDCh FGMR Joint Conference, Berlin, Germany (Poster)
    \item J.~W.~Sidabras, E.~J.~Reijerse, J.~Duan, M.~Winkler, T.~Happe, A.~Schnegg, D.~Suter, \underline{W.~Lubitz} (2019) {\em CW and Pulse EPR Studies of nano-Liter Volume [FeFe]-Hydrogenase Single Crystals Using a Novel Self-Resonant micro-Helix}, EFEPR 2019, Bratislava, Slovakia (Poster)
\end{enumerate}
