\abstrakt{Acknowledgements}

This work could not have been realized without the many people who have given me their support, mentorship, and guidance throughout this adventure. I would first like to thank Prof. Wolfgang Lubitz for his mentorship and invitation to the Max Planck Institute for Chemical Energy Conversion. This opportunity has been personally and professionally energizing. From the studying of single-crystals of enzymes to adventures in Europe. I would like to thank Prof. Dieter Suter for being my promoter and supervisor at TU Dortmund. This has been a very fruitful collaboration and I look forward to working together in the future. I thank Dr. Edward J. Reijerse for his supervision and discussion. His input to this work has been invaluable. Finally, I would like to thank Dr. Alexander Schnegg for his mentorship and the EPR Research Group for countless discussions. 

This work has been funded by the Horizon 2020 Marie Sk\l{}odowska-Curie Actions Fellowship (ActEPR; Grant No. 745702) and the Max Planck Institute. 

I would like to thank the following people for their various contributions to this body of work. 
\begin{itemize}
    \item Chapter 3: 
    \begin{itemize}
        \item Stephan Syring and Udo Klar at the Max Planck Institute for Chemical Energy Conversion and Sebastian Planckert at Max Planck Institute for Kohlenforschung for their skillfull manufacturing.
    \end{itemize}
    \item Chapter 4:
    \begin{itemize}
        \item Dr. Ryszard Narkowicz for the initial design and optimization of the SRR geometries. 
        \item Anatoly Firsov for fabricating the the SRRs geometry using an electron microscope at Helmholtz-Zentrum Berlin. 
        \item Drs. Joscha Nehrkorn and Karsten Holldack for performing the FD-FT THz experiments.
    \end{itemize}
    \item Chapters 5 and 6:
    \begin{itemize}
        \item Within the group of Prof. Thomas Happe, Drs. Jifu Duan and Martin Winkler for growing [FeFe]-hydrogenase crystals from {\em Clostridium pasteurianum} (CpI) in the H$_{ox}$ state.
        \item Within the group of Prof. Athina Zouni, Dr. Rana Hussein for growing the photosystem II complex crystals from {\em Thermosynechococcus elongatus}. 
        \item Dr. Maria Chrysina from the Max Planck Institute for Chemical Energy Conversion for guidance on photosystem II spectra.
        \item Michael Reus for the photosystem II BBY particles sample and the UV-VIS measurements.     
    \end{itemize}
\end{itemize}

Of course, none of this would be possible without the support of my family. To my parents, who taught me to tackle every problem head-on, and to my brother, . I give my undying gratitude to my wife, Emily, who has kept me grounded while providing a loving home. And to my daughter, Juniper, who's smile and curiosity inspires me to push further.
 